\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Kyle Rego}
\address{ Raynham, MA 02767  }
\address{ regoky@outlook.com \\ https://kylerego.github.io }

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Experience}

  \begin{rSubsection}{Impero Software}{June 2022 - Present}{Software Engineer}{Remote}
      \item Maintaining a large Ruby on Rails monolith and services. \item Discovered the cause of and fixed an insidious bug related to paginated data from an internal web service API that had affected hundreds of customers for years.
      \item Refactored a daily cron job to decrease the memory increase in one step from 1.8Gb to 500Mb (while fixing an unrelated bug). 
      \item Completed a large part of the work allowing easy configuration of per-school user permissions/settings/ feature access schedules from a single dashboard for the entire school district.
      \item Rapidly developed the back-end service for a merge duplicate student support tool (merging data from 40+ tables) with reflections/introspection of the model associations and business logic.
  \end{rSubsection}

    \begin{rSubsection}{Symmetry Scribes}{April 2019 - March 2020}{Medical Scribe}{Wareham, MA}
    \item Assisting physicians in the Emergency Department by writing clinical documentation.
    \end{rSubsection}

    % \begin{rSubsection}{Swansea Ambulance Corps}{June 2017 - February 2020}{Emergency Medical Technician}{Swansea, MA}
    % \item Staffing an Advanced Life Support ambulance providing emergency medical services to a town of about 15,000 residents.
    % \end{rSubsection}
  
  \end{rSection}

  \begin{rSection}{Education}

    % {\bf Launch School} \hfill {\em December 2021 - \em June 2022} \\
    % Web development \\
    % Completed all of the core curriculum except for the last course

    % {\bf Quinnipiac University School of Medicine} \hfill {\em August 2020 - \em May 2021} \\
    % Medical student

    {\bf Rensselaer Polytechnic Institute (RPI)} \hfill {\em August 2015 - December 2018} \\ 
    Bachelor of Science in Physics  \\
    Overall GPA: 4.0
  \end{rSection}

  \begin{rSection}{Technical Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer languages & Ruby, SQL, HTML, CSS, JavaScript, RSpec, Capybara, Python \\
      % Protocols \& APIs & XML, JSON, SOAP, REST \\
      % Databases & MySQL, PostgreSQL, Microsoft SQL \\
      Software and tools & Git, Ruby on Rails, Hotwire, Cucumber, PyQt \\
      Skills & Object-oriented programming, Test-driven development \\
    \end{tabular}
  \end{rSection}

  \begin{rSection}{Projects}
    \begin{rSubsection}{Anki Books/Anki Record}{2023}{}{}
        \item Anki Books (ankibooks.io) is a note-taking and flashcards Rails application. Anki Record is a Ruby gem providing an API to Anki flashcard deck packages (zipped SQLite databases) developed to be used in the Rails app.
        \item Wrote hundreds of unit tests and feature tests with RSpec, Cucumber, and Capybara including testing file uploading, reordering flashcards with the HTML drag and drop API, and code syntax highlighting.
    \end{rSubsection}
        
    % \begin{rSubsection}{Anki add-ons}{2021}{}{}
    %     \item Add-ons for the cross-platform desktop flashcard application Anki developed with Python and PyQt. These add a magnifying glass mouse cursor feature and a tool to easily create cards that together constitute an enumeration.
    % \end{rSubsection}  
  \end{rSection}

  \begin{rSection}{Honors}
  
    {\bf The J. Erik Jonsson Prize} \hfill {\em May 2019} \\
    Awarded at Commencement to the senior who has achieved the highest academic record in the class.
    
  \end{rSection}

\end{document}